# E2



```{r , include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, result='asis', fig.width = 8, dev='tikz')
 
 library(ggplot2)
 library(plotly)
 library(tidyverse)
 library(htmlwidgets)
 library(pander)
 #library(latex2exp)
 library(knitr)
 library(dplyr) #data frame manipulation
 require(scales) # to access break formatting functions
 #library(shiny)
 #library(shinyWidgets)
 library(ggrepel)
 library(Rose)
 library(widgetframe)
 require("processx")
 library(webshot)
 library(htmltools)
 #library(sigma)
 source('functions.R')
```



the two particle operator can be defined at zero momentum

$$
O_2=\phi(0)\phi(0)
$$ We can also construct an operator that interpolates the same state

#### FT

we define the discrete Fourier Tansform  in space

$$
\phi(p,t)=\frac{1}{V}\sum_x e^{i2\pi \vec{p}\cdot \vec{x}/L}\phi(x,t)
$$
with $\vec{p}=(n_x,n_y,n_z)$ and $n_i=0,1,...,L-1$
since the field  $\phi(x,t)$ is real we have that 
$$
\phi(-p,t)=\phi^*(p,t)
$$




with back to back momentum. In the latter case to have an operator which
projected on the $A1$ irrep of $O(24)$ we need to construct the
combination
$$
O_2^{A1}=\frac{1}{\sqrt{3}}\left[\phi(p_x)\phi^*(p_x)+\phi(p_y)\phi^*(p_y)+\phi(p_z)\phi^*(p_z)\right]
$$ 
where $p_x=(2\pi /L,0,0)$ and we use the fact that
$\phi(-p)=\phi(p)^*$.

with these Operator we can construct the correlator $$
\frac{1}{T}\sum_{t_1}\langle O_2^{A1}(t_1) O_2^{A1*}(t_1+t)\rangle = |A_{0\to2}| \left( e^{-E_2 t}+e^{-E_2 (T-t)}\right)+
|A_{1\to1}| e^{-E_1 t}
$$

-   $E_2$ is the energy of the two particle state at rest;

-   $E_1$ is the energy of the single particle with momentum
    $|p|=2\pi/L$;

-   $O_2^{A1*}=O_2^{A1}$ since it is real.

#### E irrep

The other irrep possible is $E$ which is two dimensional
$$
O_2^{E1}=\frac{1}{\sqrt{2}}\left[\phi(p_x)\phi(p_x)^*-\phi(p_y)\phi(p_y)^*\right]
$$
which should interpolate an exited state, the other state of this irrep is
$$
O_2^{E2}=\frac{1}{\sqrt{2}}\left[\phi(p_x)\phi(p_x)^*+\phi(p_y)\phi(p_y)^*-2\phi(p_z)\phi(p_z)^*\right]
$$

#### two particle with momentum operator

#### p=(1,0,0)

we can construct the two particle operator with momentum as
$$
O_{2p_x}=\phi(p_x)\phi(0)  \,,\quad p_x=(1,0,0)
$$
this operator is already in the irrep $A1$. The two particle correlator can be define as
$$
\langle O_{2p_x} O_{2p_x}^\dagger(t)\rangle =  |A_{0\to2}|^2 \left( e^{-E_{2p_x} t}+e^{-E_{2p_x} (T-t)}\right)+
|A_{\phi(0)\to\phi(p_x)}|^2 \left(e^{-\omega_{p_x} T-m t+\omega_{p_x}t}+e^{-m T-\omega_{p_x} t+mt} \right)\,.
$$
We can average over all the direction to have a more precise correlator
$$
\frac{1}{3}\sum_{i=x,y,z} \langle O_{2p_i} O_{2p_i}^\dagger(t)\rangle
$$

#### p=(1,1,0)

$$
O_{2p_{xy}}=\phi(p_{xy})\phi(0)  \,,\quad p_{xy}=(1,1,0)
$$
To construct the correlator we can average over all the direction to have a more precise correlator
$$
\frac{1}{3}\sum_{i=xy,yz,zx} \langle O_{2p_i} O_{2p_i}^\dagger(t)\rangle
$$

#### p=(1,1,1)

The operator
$$
O_{2p_{xyx}}=\phi(p_{xyz})\phi(0)  \,,\quad p_{xyz}=(1,1,1)\,,
$$
and the correlator
$$
 \langle O_{2p_{x,y,z}} O_{2p_{x,y,z}}^\dagger(t)\rangle
$$

## Plot


```{r, echo=FALSE,results='asis'}


TLs<-list(c(48,30), c(96,30)  )
momenta<-list(c(0,0,0,0,0,0),c(1,0,0,0,0,0),c(1,1,0,0,0,0),c(1,1,1,0,0,0))
p2<-c()
E1s<-c()
E1serr<-c()
cont_disp<-c()
latt_disp<-c()

for (TL in TLs){
gg<-ggplot()

T<- TL[1]
L<- TL[2]
dir<-paste("../out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
m<-get_energy("E2_0",all_obs,mt)[1]  

for (ip in momenta){
  p2<-c(p2,  (2*pi/L)^2*(ip[1]^2+ip[2]^2+ip[3]^2   )  )
  cont_disp<-c(cont_disp, sqrt((m/2)^2+(2*pi/L)^2*(ip[1]^2+ip[2]^2+ip[3]^2)  )+m/2   )
  hatp2=4* (sin(pi*ip[1]/L)^2+sin(pi*ip[2]/L)^2+sin(pi*ip[3]/L)^2   )
  #latt_disp<-c(latt_disp, acosh(1+ 0.5*(m^2+hatp2))  )
  latt_disp<-c(latt_disp, acosh(cosh(m/2)  +0.5*hatp2 )+m/2    )
}

gg<-add_plot("E2_0",all_obs,mt,gg,"no")
tmp<-get_energy("E2_0",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
gg<-add_plot("E2_0_p1",all_obs,mt,gg,"yes")
tmp<-get_energy("E2_0_p1",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
gg<-add_plot("E2_0_p11",all_obs,mt,gg,"yes")
tmp<-get_energy("E2_0_p11",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
gg<-add_plot("E2_0_p111",all_obs,mt,gg,"yes")
tmp<-get_energy("E2_0_p111",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
gg<-add_plot("E2_0_A1",all_obs,mt,gg,"no")
fig<-ggplotly(gg)%>%config(mathjax='cdn') %>% layout(title="fit" ,xaxis = list(title = "$t$",showexponent = "all", exponentformat = "e" , range=c(0, 14), autorange = F  ) ,
                      yaxis = list(title = "$\\log c(t)$",showexponent = "all", exponentformat = "e", autorange = T  ))  
print(htmltools::tagList(fig))

}



df <-data.frame("p2"=p2,"E1"=E1s,"E1err"=E1serr, "cont_disp"=cont_disp , "latt_disp"=latt_disp)
#g1<- ggplot()+ geom_point(df ,mapping= aes(x=p2, y=E1)  )+
#  geom_errorbar(df ,mapping= aes(x=p2, ymin=E1-E1err, ymax=E1+E1err),width=0.005  )+ theme_bw()+
#  geom_line(df ,mapping= aes(x=p2, y=cont_disp,,color="cont"))+
#  geom_line(df ,mapping= aes(x=p2, y=latt_disp,color="lattice"))
#ggplotly(g1)%>%layout(title="dispersion relation" ,xaxis = list(title = TeX("p^2"),showexponent = "all", exponentformat = "e" ,  autorange = T  ) ,
#                      yaxis = list(title = TeX("E_2(P)"),showexponent = "all", exponentformat = "e", autorange = T  )) 
```

### residual plot 

```{r, echo=FALSE,results='asis'}


TLs<-list(c(48,30) , c(96,30) )

for (TL in TLs){
  gg<-ggplot()

T<- TL[1]
L<- TL[2]
dir<-paste("../out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

gg<-add_res_plot("E2_0",all_obs,mt,gg,"no")
gg<-add_res_plot("E2_0_p1",all_obs,mt,gg,"no")
gg<-add_res_plot("E2_0_p11",all_obs,mt,gg,"no")
gg<-add_res_plot("E2_0_p111",all_obs,mt,gg,"no")
gg<-add_res_plot("E2_0_A1",all_obs,mt,gg,"no")

fig<-ggplotly(gg,dynamicTicks = TRUE)%>%config(mathjax='cdn') %>% layout(title="fit" ,xaxis = list(title = "$t$",showexponent = "all", exponentformat = "e" ,  autorange = T  ) ,
                      yaxis = list(title = "res $c(t)$",showexponent = "all", exponentformat = "e", autorange = T  ))  
print(htmltools::tagList(fig))

}


```



## Weight shift

Here we compute the two particle energy with a different procedure. Starting from the correlator

$$
\langle O_{2p_x} O_{2p_x}^\dagger(t)\rangle =  |A_{0\to2}|^2 \left( e^{-E_{2p} t}+e^{-E_{2p} (T-t)}\right)+
|A_{\phi(0)\to\phi(p)}|^2 \left(e^{-\omega_{p} T-m t+\omega_{p}t}+e^{-m T-\omega_{p} t+mt} \right)\\
=|A_{0\to2}|^2 e^{-E_{2p} \frac{T}{2}} \cosh\left(E_{2p}(t-\frac{T}{2}) \right)+
|A_{\phi(0)\to\phi(p)}|^2 e^{-(\omega_p+m ) \frac{T}{2}} \cosh\left((\omega_p-m )(t-\frac{T}{2}) \right)
$$
We divide the correlator by the exponential of the termal pollution term
$$
c_w(t)=\frac{c(t)}{e^{-(\omega_p+m ) \frac{T}{2}} \cosh\left((\omega_p-m )(t-\frac{T}{2}) \right)}
$$
then we do a shift of the correlator
$$
c_{ws}(t)=c_w(t+1)-c_w(t)
$$
in this way we eliminate the dependence over $|A_{\phi(0)\to\phi(p)}|^2$ and we fit the two parameters $E_2$ and $A_{0\to2}$ 
$$
c_{ws}(t)=|A_{0\to2}|^2 \left\{\frac{e^{-E_{2p} \frac{T}{2}} \cosh\left(E_{2p}(t+1-\frac{T}{2}) \right)}
{e^{-(\omega_p+m ) \frac{T}{2}} \cosh\left((\omega_p-m )(t+1-\frac{T}{2}) \right)}-
\frac{e^{-E_{2p} \frac{T}{2}} \cosh\left(E_{2p}(t-\frac{T}{2}) \right)}
{e^{-(\omega_p+m ) \frac{T}{2}} \cosh\left((\omega_p-m )(t-\frac{T}{2}) \right)}
\right\}
$$


```{r, echo=FALSE,results='asis'}


TLs<-list(c(48,30) , c(96,30) )

momenta<-list(c(0,0,0,0,0,0),c(1,0,0,0,0,0),c(1,1,0,0,0,0),c(1,1,1,0,0,0))
p2<-c()
E1s<-c()
E1serr<-c()
cont_disp<-c()
latt_disp<-c()

for (TL in TLs){
gg<-ggplot()
T<- TL[1]
L<- TL[2]
dir<-paste("../out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
m<-get_energy("E2_0",all_obs,mt)[1]  

for (ip in momenta){
  p2<-c(p2,  (2*pi/L)^2*(ip[1]^2+ip[2]^2+ip[3]^2   )  )
  cont_disp<-c(cont_disp, sqrt((m/2)^2+(2*pi/L)^2*(ip[1]^2+ip[2]^2+ip[3]^2)  )+m/2   )
  hatp2=4* (sin(pi*ip[1]/L)^2+sin(pi*ip[2]/L)^2+sin(pi*ip[3]/L)^2   )
  #latt_disp<-c(latt_disp, acosh(1+ 0.5*(m^2+hatp2))  )
  latt_disp<-c(latt_disp, acosh(cosh(m/2)  +0.5*hatp2 )+m/2    )
}

gg<-add_plot("E2_0",all_obs,mt,gg,"no")
tmp<-get_energy("E2_0",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
gg<-add_plot("E2_0_p1_ws",all_obs,mt,gg,"no")
tmp<-get_energy("E2_0_p1_ws",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
gg<-add_plot("E2_0_p11_ws",all_obs,mt,gg,"no")
tmp<-get_energy("E2_0_p11_ws",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
gg<-add_plot("E2_0_p111_ws",all_obs,mt,gg,"no")
tmp<-get_energy("E2_0_p111_ws",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
gg<-add_plot("E2_0_A1",all_obs,mt,gg,"no")



fig<- ggplotly(gg)%>%config(mathjax='cdn')%>% layout(title="fit" ,xaxis = list(title = "$t$",showexponent = "all", exponentformat = "e" , range=c(0, 14), autorange = F  ) ,
                      yaxis = list(title = "$ c(t)$",showexponent = "all", exponentformat = "e", autorange = T  ))  
print(htmltools::tagList(fig))

df <-data.frame("p2"=p2,"E1"=E1s,"E1err"=E1serr, "cont_disp"=cont_disp , "latt_disp"=latt_disp)

}
#g1<- ggplot()+ geom_point(df ,mapping= aes(x=p2, y=E1)  )+
#  geom_errorbar(df ,mapping= aes(x=p2, ymin=E1-E1err, ymax=E1+E1err),width=0.005  )+ theme_bw()+
#  geom_line(df ,mapping= aes(x=p2, y=cont_disp,,color="cont"))+
#  geom_line(df ,mapping= aes(x=p2, y=latt_disp,color="lattice"))
#ggplotly(g1)%>%layout(title="dispersion relation" ,xaxis = list(title = TeX("p^2"),showexponent = "all", exponentformat = "e" ,  autorange = T  ) ,
#                      yaxis = list(title = TeX("E_2(P)"),showexponent = "all", exponentformat = "e", autorange = T  )) 
```

### Residual plot Ws 

```{r, echo=FALSE,results='asis'}


TLs<-list(c(48,30) , c(96,30)  )

for (TL in TLs){
gg<- ggplot()
T<- TL[1]
L<- TL[2]
dir<-paste("../out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
m<-get_energy("E2_0",all_obs,mt)[1]  

gg<-add_res_plot("E2_0",all_obs,mt,gg,"no")
gg<-add_res_plot("E2_0_p1_ws",all_obs,mt,gg,"no")
gg<-add_res_plot("E2_0_p11_ws",all_obs,mt,gg,"no")
gg<-add_res_plot("E2_0_p111_ws",all_obs,mt,gg,"no")
gg<-add_res_plot("E2_0_A1",all_obs,mt,gg,"no")

fig<-ggplotly(gg, dynamicTicks = TRUE)%>%config(mathjax='cdn')%>% layout(title="fit" ,xaxis = list(title = "$t$",showexponent = "all", exponentformat = "e" ,  autorange = T  ) ,
                      yaxis = list(title = "res $ c(t)$",showexponent = "all", exponentformat = "e",range=c(-1,1), autorange = F  ))  
print(htmltools::tagList(fig))

}


df <-data.frame("p2"=p2,"E1"=E1s,"E1err"=E1serr, "cont_disp"=cont_disp , "latt_disp"=latt_disp)

```


## Compare the two methods for E2  

```{r, echo=FALSE,results='asis'}


TLs<-list(c(48,30) , c(96,30) )

momenta<-list(c(0,0,0,0,0,0),c(1,0,0,0,0,0),c(1,1,0,0,0,0),c(1,1,1,0,0,0))

for (TL in TLs){
p2<-c()
E1s<-c()
E1serr<-c()
cont_disp<-c()
latt_disp<-c()
ws<-c()
gg<-ggplot()
T<- TL[1]
L<- TL[2]
dir<-paste("../out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
m<-get_energy("E2_0",all_obs,mt)[1]  

for (ip in momenta){
  p2<-c(p2,  (2*pi/L)^2*(ip[1]^2+ip[2]^2+ip[3]^2   )  )
  cont_disp<-c(cont_disp, sqrt((m/2)^2+(2*pi/L)^2*(ip[1]^2+ip[2]^2+ip[3]^2)  )+m/2   )
  hatp2=4* (sin(pi*ip[1]/L)^2+sin(pi*ip[2]/L)^2+sin(pi*ip[3]/L)^2   )
  #latt_disp<-c(latt_disp, acosh(1+ 0.5*(m^2+hatp2))  )
  latt_disp<-c(latt_disp, acosh(cosh(m/2)  +0.5*hatp2 )+m/2    )
}


tmp<-get_energy("E2_0",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
tmp<-get_energy("E2_0_p1",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
tmp<-get_energy("E2_0_p11",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
tmp<-get_energy("E2_0_p111",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
tmp<-get_energy("E2_0_A1",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])

tmp<-get_energy("E2_0_p1_ws",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
tmp<-get_energy("E2_0_p11_ws",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
tmp<-get_energy("E2_0_p111_ws",all_obs,mt);E1s<-c(E1s,tmp[1]);E1serr<-c(E1serr,tmp[2])
ws<-c(ws,"2par","3par","3par","3par","2par","ws","ws","ws" )

df <-data.frame("p2"=p2,"E1"=E1s,"E1err"=E1serr, "ws"=ws ,  "cont_disp"=cont_disp , "latt_disp"=latt_disp)

g1<- ggplot()+ geom_point(df ,mapping= aes(x=p2, y=E1 ,color=ws)  )+
geom_errorbar(df ,mapping= aes(x=p2, ymin=E1-E1err, ymax=E1+E1err, color=ws),width=0.005  )+ theme_bw()
#  geom_line(df ,mapping= aes(x=p2, y=cont_disp,,color="cont"))+
#  geom_line(df ,mapping= aes(x=p2, y=latt_disp,color="lattice"))
fig<-ggplotly(g1)%>%layout(title="dispersion relation" ,xaxis = list(title = TeX("p^2"),showexponent = "all", exponentformat = "e" ,  autorange = T  ) ,
                      yaxis = list(title = TeX("E_2(P)"),showexponent = "all", exponentformat = "e", autorange = T  )) 
print(htmltools::tagList(fig))
}

```


```{r }
library(ggplot2)
library(plotly)
df <- data.frame(x = 1:5, y = 1:5)    
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knitr handle the rendering naturally
```

