# E2 connected {#E2connected}



```{r , include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, result='asis')
 
 library(ggplot2)
 library(plotly)
 library(tidyverse)
 library(htmlwidgets)
 library(pander)
 #library(latex2exp)
 library(knitr)
 library(dplyr) #data frame manipulation
 require(scales) # to access break formatting functions
 #library(shiny)
 #library(shinyWidgets)
 library(ggrepel)
 library(Rose)
 library(widgetframe)
 require("processx")
 library(webshot)
 library(htmltools)
 #library(sigma)
 source('functions.R')
```


We define the generator of the correlation function as 
$$
  Z[J_0,J_1]=N\int D\phi_0D\phi_1 e^{-S+\int J_0\phi_0+\int J_1\phi_1} \,.
$$
with $N=1/Z[0,0]$ such that $Z[0,0]=1$.
the correlation function acting with derivativesrespect to $J$ and then setting it to zero, for example
$$
\langle \phi_0(x)^2 \phi_0(y)^2\rangle=
\frac{\partial^2}{\partial^2 J_0(x)}\frac{\partial^2}{\partial^2 J_0(y)}Z[J_0,J_1]\bigg|_{J_0=J_1=0}\,.
$$
We can define the connected correlation function deriving logarithm of $Z$ i.e.
$$
\langle \phi_0(x)^2 \phi_0(y)^2\rangle_c=
\frac{\partial^2}{\partial^2 J_0(x)}\frac{\partial^2}{\partial^2 J_0(y)}\log Z[J_0,J_1]\bigg|_{J_0=J_1=0}\\
=\langle \phi_0(x)^2 \phi_0(y)^2\rangle-\langle \phi_0(x) \phi_0(y)\rangle^2
-\langle \phi_0(x)^2\rangle\langle \phi_0(y)^2\rangle
$$
we use the fact that $\langle \phi (x)\rangle=0$.


Below we plot the effective mass computed from 

- $\langle \phi_0(x)^2 \phi_0(y)^2\rangle$
- $\langle \phi_0(x)^2 \phi_0(y)^2\rangle-\langle \phi_0(x) \phi_0(y)\rangle^2$
- $\langle \phi_0(x) \phi_0(y)\rangle^2$

In all cases we remove the constant $\langle \phi_0(x)^2\rangle$ term shifting the correlator.




```{r, echo=FALSE,results='asis'}



gg<-ggplot()
T<- 32
L<- 24
 dir<-paste("../out")
 file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
 
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)


 gg<-add_plot("E2_0",all_obs,mt,gg,"no")
 gg<-add_plot("E2_0_con",all_obs,mt,gg,"no")
 gg<-add_plot("E1_0_sq",all_obs,mt,gg,"no")
 gg1<-ggplot()
 gg1<-add_plot("E1_0",all_obs,mt,gg1,"no")

fig<- myplotly(gg,"fit","t","$m_{eff}$"  )


```


### FT $\phi^2$

Below we add to the plot the FT of the operator $\phi(x)^2$ difined as

$$
  \widetilde{\phi(t,p)^2}=\sum_{\vec x}\phi(t,\vec x)^2 e^{i\vec{p}\cdot\vec{x}}
$$
we call its effective mass E2_0_p0

```{r, echo=FALSE,results='asis'}


gg<-ggplot()
T<- 64
L<- 28
dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)
 
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)


 gg<-add_plot("E2_0",all_obs,mt,gg,"no")
 gg<-add_plot("E2_0_con",all_obs,mt,gg,"no")
 gg<-add_plot("E1_0_sq",all_obs,mt,gg,"no")
gg<-add_plot("E2_0_p0",all_obs,mt,gg,"no")

 gg1<-ggplot()
 gg1<-add_plot("E1_0",all_obs,mt,gg1,"no")

fig<- myplotly(gg,"fit","t","$m_{eff}$" ,yrange=c(0,2) )


```


### Test ensemble


```{r, echo=FALSE, eval=FALSE,results='asis' ,dev='tikz'}
library(Rose)
gg<-ggplot()
T<- 16
L<- 8
 dir<-paste("/home/marco/programs/Z2-phi4/build/main/data/out")
 file=sprintf("%s/G2t_T%d_L%d_msq0-4.850000_msq1-4.850000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
 
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)



 gg<-add_plot("E2_0",all_obs,mt,gg,"no")
 gg<-add_plot("E2_0_con",all_obs,mt,gg,"no")
 gg<-add_plot("E1_0_sq",all_obs,mt,gg,"no")
 gg<-add_plot("E2_0_p0",all_obs,mt,gg,"no")
 gg1<-ggplot()
 gg1<-add_plot("E1_0",all_obs,mt,gg1,"no")

fig<- myplotly(gg,"fit","t","$m_{eff}$"  )
#fig<- myplotly(gg,"fit","t", "y", width=900, yrange = c(-3,5) )

```