# GEVP g0.025 {#GEVPg0_025}

```{r  include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, result='asis')
 
 library(ggplot2)
 library(plotly)
 library(tidyverse)
 library(htmlwidgets)
 library(pander)
 #library(latex2exp)
 library(knitr)
 library(dplyr) #data frame manipulation
 require(scales) # to access break formatting functions
 #library(shiny)
 #library(shinyWidgets)
 library(ggrepel)
 library(Rose)
 library(widgetframe)
 require("processx")
 library(webshot)
 library(htmltools)
 #library(sigma)
 source('functions.R')
```

with the term $g\phi_0^3\phi_1$ we expect the following spectral decomposition  
$$
\langle\phi_1(0)\phi_1(t) \rangle  \approx |\langle 0|\phi_1|\phi_1\rangle|^2| \left( e^{-M_1t}+e^{-M_1(T-t)}\right) 
+|\langle 0|\phi_1|\phi_0\rangle|^2 \left( e^{-Mt}+e^{-M(T-t)}\right)\\
+|\langle 0|\phi_1|\phi_0^3\rangle|^2 \left( e^{-E_3t}+e^{-E_3(T-t)}\right)
+|\langle \phi_0|\phi_1|\phi_0^2\rangle|^2 e^{-(M)T} \left( e^{-(E_2-M)t}+e^{-(E_2-M)(T-t)}\right)\,.
$$

Together with the previous correlator we have $\langle\phi_0(0)\phi_0(t) \rangle$ and $\langle\phi_0^3(0)\phi_0^3(t) \rangle$ which interpolates the same states. However the relevant states should be

$$
\langle\phi_0(0)\phi_0(t) \rangle \approx |A_{\phi_0\to\phi_0}| \left( e^{-Mt}+e^{-M(T-t)}\right)
$$

and the other should be suppressed. While

$$
\langle\phi_0^3(0)\phi_0^3(t) \rangle \approx |A_{\phi_0^3\to\phi_0^3}|  \left( e^{-E_3t}+e^{-E_3(T-t)}\right)+ 
|A_{\phi_0\to\phi_0}| \left( e^{-Mt}+e^{-M(T-t)}\right)\\
+|A_{\phi_0\to\phi_0^2}| e^{-(M)T} \left( e^{-(E_2-M)t}+e^{-(E_2-M)(T-t)}\right)\,.
$$


We construct the matrix 

$$
C(t)=\begin{pmatrix}
\langle\phi_0(0)\phi_0(t) \rangle  & \langle\phi_0^3(0)\phi_0(t)  & \langle\phi_0(0)\phi_1(t) \rangle   \rangle  \\
 & \langle\phi_0^3(0)\phi_0^3(t) \rangle  & \langle\phi_0^3(0)\phi_1(t) \rangle \\
 & &\langle\phi_1(0)\phi_1(t) \rangle  
\end{pmatrix}
$$
the matrix since $C$ is hermitiian  so the lower triangular non-written part can be computed as $C_{ij}=C_{ji}^*$.

We solve the GEVP
$$
  C(t)v_n(t,t_0)=\lambda_n(t,t_0)C(t_0) v_n(t,t_n)
$$
We fit $\lambda_n(t,t_0)$ as
$$
\lambda_n(t,t_0)=C \left(e^{ - E_n  (t-t_0)}  + e^{ - E_n  ((T - t)-t_0)}\right)
$$

We also consider the case where we add an other operato to the GEVP

We construct the matrix 

$$
C(t)=\begin{pmatrix}
\langle\phi_0(0)\phi_0(t) \rangle  & \langle\phi_0^3(0)\phi_0(t)  & \langle\phi_0(0)\phi_1(t) \rangle   \rangle &\langle\phi_0(0) O_{A1}(t) \rangle \\
 & \langle\phi_0^3(0)\phi_0^3(t) \rangle  & \langle\phi_0^3(0)\phi_1(t) \rangle  &\langle\phi_0^3(0) O_{A1}(t) \rangle\\
 & &\langle\phi_1(0)\phi_1(t) \rangle  &\langle\phi_1(0) O_{A1}(t) \rangle \\
&& &\langle O_{A1} (0) O_{A1}(t) \rangle
\end{pmatrix}
$$


```{r, echo=FALSE,results='asis'}


gg<-ggplot()
T<- 32
L<- 28
# dir<-paste("../out")
# file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

file_meff=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_meff_correlators",dir,T,L)

mt_meff<-read_df(file_meff)
all_obs_meff<- get_all_corr(mt_meff)
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

#gg<-add_plot("E3_0_vev",all_obs,mt,gg,"yes")
#gg<-add_plot("E3_0_p1",all_obs,mt,gg,"yes")
#gg<-add_plot("E3_0_p11",all_obs,mt,gg,"yes")
#gg<-add_plot("E3_0_p111",all_obs,mt,gg,"yes")

# gg<-add_plot("GEVP_phi0_phi03_phi1_l0",all_obs,mt,gg,"yes")
# gg<-add_plot("GEVP_phi0_phi03_phi1_l1",all_obs,mt,gg,"yes")
# gg<-add_plot("GEVP_phi0_phi03_phi1_l2",all_obs,mt,gg,"yes")

 gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
 gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
 gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
 gg<-add_plot("E1_0",all_obs,mt,gg,"no")
 gg<-add_plot("E1_1",all_obs,mt,gg,"no")
 gg1<-add_plot("E3_0",all_obs_meff,mt_meff,gg,"no",6)

fig<- myplotly(gg,"fit","t", "y", to_print=TRUE, width = 900 )


```


```{r, echo=FALSE,results='asis'}
df<-data.frame("L"=c(0),"T"=c(0),"E3"=c(0),"E3err"=c(0),"E1"=c(0),"E1err"=c(0),
               "E3p1"=c(0),"E3p1err"=c(0),"E1p1"=c(0),"E1p1err"=c(0))
gg<-ggplot()
T<- 64
L<- 24

dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0",all_obs,mt,gg,"no")
gg<-add_plot("E1_1",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_vev",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl0",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl1",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl2",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl3",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )

df[length(df[,1])+1,]<-list(L,T,
                          get_energy("E3_0_vev",all_obs,mt)[1],
                          get_energy("E3_0_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[2],
                          get_energy("E3_0_p1_vev",all_obs,mt)[1],
                          get_energy("E3_0_p1_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[2]
                          )


```



```{r, echo=FALSE,results='asis'}

T<- 128
L<- 24

dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0",all_obs,mt,gg,"no")
gg<-add_plot("E1_1",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_vev",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl0",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl1",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl2",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl3",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )

df[length(df[,1])+1,]<-list(L,T,
                          get_energy("E3_0_vev",all_obs,mt)[1],
                          get_energy("E3_0_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[2],
                          get_energy("E3_0_p1_vev",all_obs,mt)[1],
                          get_energy("E3_0_p1_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[2]
                          )


```

```{r, echo=FALSE,results='asis'}

df<-df[-1,] 
gg<-ggplot()
T<- 64
L<- 28

dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0",all_obs,mt,gg,"no")
gg<-add_plot("E1_1",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_vev",all_obs,mt,gg,"no")



fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )

df[length(df[,1])+1,]<-list(L,T,
                          get_energy("E3_0_vev",all_obs,mt)[1],
                          get_energy("E3_0_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[2],
                          get_energy("E3_0_p1_vev",all_obs,mt)[1],
                          get_energy("E3_0_p1_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[2]
                          )

```


```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 64
L<- 32

dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0",all_obs,mt,gg,"no")
gg<-add_plot("E1_1",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_vev",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl0",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl1",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl2",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl3",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )

df[length(df[,1])+1,]<-list(L,T,
                          get_energy("E3_0_vev",all_obs,mt)[1],
                          get_energy("E3_0_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[2],
                          get_energy("E3_0_p1_vev",all_obs,mt)[1],
                          get_energy("E3_0_p1_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[2]
                          )


```

```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 64
L<- 34

dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0",all_obs,mt,gg,"no")
gg<-add_plot("E1_1",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_vev",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl0",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl1",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl2",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl3",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )

df[length(df[,1])+1,]<-list(L,T,
                          get_energy("E3_0_vev",all_obs,mt)[1],
                          get_energy("E3_0_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[2],
                          get_energy("E3_0_p1_vev",all_obs,mt)[1],
                          get_energy("E3_0_p1_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[2]
                          )


```

```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 64
L<- 36

dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0",all_obs,mt,gg,"no")
gg<-add_plot("E1_1",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_vev",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl0",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl1",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl2",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_meffl3",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )

df[length(df[,1])+1,]<-list(L,T,
                          get_energy("E3_0_vev",all_obs,mt)[1],
                          get_energy("E3_0_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[2],
                          get_energy("E3_0_p1_vev",all_obs,mt)[1],
                          get_energy("E3_0_p1_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[2]
                          )


```



```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 64
L<- 40

dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0",all_obs,mt,gg,"no")
gg<-add_plot("E1_1",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_vev",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl0",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl1",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl2",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_meffl3",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )

df[length(df[,1])+1,]<-list(L,T,
                          get_energy("E3_0_vev",all_obs,mt)[1],
                          get_energy("E3_0_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt)[2],
                          get_energy("E3_0_p1_vev",all_obs,mt)[1],
                          get_energy("E3_0_p1_vev",all_obs,mt)[2],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[1],
                          get_energy("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt)[2]
                          )


```



```{r}
gg<-ggplot()
gg<- gg+ geom_point(data=df,mapping=aes(x=L, y=E3, color="$3\\phi_0$"))
gg<- gg+ geom_errorbar(data=df,mapping=aes(x=L, ymin=E3-E3err, ymax=E3+E3err, color="$3\\phi_0$"), width=0.3)
gg<- gg+ geom_point(data=df,mapping=aes(x=L, y=E1, color="$\\phi_1$"))
gg<- gg+ geom_errorbar(data=df,mapping=aes(x=L, ymin=E1-E1err, ymax=E1+E1err, color="$\\phi_1$"), width=0.3)
myplotly(gg,"","L","E(p=(0,0,0))",to_print=FALSE)
```


## P=(1,0,0)

When the total momentum is $\vec p=(1,0,0)$ the possible states are

$$
|A_{0-\phi_1}|^2 \left( e^{-E_{\phi_1}t}+e^{-E_{\phi_1}(T-t)}\right) 
+|A_{0-\phi_0}|^2 \left( e^{-E_{\phi_0}t}+e^{-E_{\phi_0}(T-t)}\right)\\
+|A_{0-3\phi_0}|^2 \left( e^{-E_{3\phi_0}t}+e^{-E_{3\phi_0}(T-t)}\right)\\
+|A_{\phi_0-2\phi_0(p)}|^2 e^{-E_{\phi_0}T} \left( e^{-(E_{2\phi_0}(p)-E_{\phi_0})t}+e^{-(E_{2\phi_0}(p)-E_{\phi_0})(T-t)}\right)\\
+|A_{\phi_0(p)-2\phi_0}|^2 e^{-E_{\phi_0}(p)T} \left( e^{-(E_{2\phi_0}-E_{\phi_0}(p))t}+e^{-(E_{2\phi_0}-E_{\phi_0}(p))(T-t)}\right)\,.
$$
In particular the last term has an effective mass of $E_{2\phi_0}-E_{\phi_0}(p)<E_{\phi_0}$



```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 64
L<- 24
dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0_p1",all_obs,mt,gg,"no")
gg<-add_plot("E1_1_px",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_p1_vev",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_p1_meffl0",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_p1_meffl1",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_p1_meffl2",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_p1_meffl3",all_obs,mt,gg,"no")

#gg<-add_plot("E2_0_p1_ws",all_obs,mt,gg,"no")
#gg<-add_plot("E2_0",all_obs,mt,gg,"no")
#gg<-add_plot("E1_0",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )


```

```{r, echo=FALSE,results='asis'}


gg<-ggplot()
T<- 64
L<- 28
dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0_p1",all_obs,mt,gg,"no")
gg<-add_plot("E1_1_px",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_p1_vev",all_obs,mt,gg,"no")
#gg<-add_plot("E2_0_p1_ws",all_obs,mt,gg,"no")
#gg<-add_plot("E2_0",all_obs,mt,gg,"no")
#gg<-add_plot("E1_0",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )


```



```{r, echo=FALSE,results='asis'}


gg<-ggplot()
T<- 64
L<- 32
dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0_p1",all_obs,mt,gg,"no")
gg<-add_plot("E1_1_px",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_p1_vev",all_obs,mt,gg,"no")

fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )


```



```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 64
L<- 40
dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0_p1",all_obs,mt,gg,"no")
gg<-add_plot("E1_1_px",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_p1_vev",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_p1_meffl0",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_p1_meffl1",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_p1_meffl2",all_obs,mt,gg,"no")
# gg<-add_plot("GEVP_0_3_1_A1_p1_meffl3",all_obs,mt,gg,"no")

#gg<-add_plot("E2_0_p1_ws",all_obs,mt,gg,"no")
#gg<-add_plot("E2_0",all_obs,mt,gg,"no")
#gg<-add_plot("E1_0",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )


```



```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 128
L<- 24
dir<-paste("../../g0.025/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0_p1",all_obs,mt,gg,"no")
gg<-add_plot("E1_1_px",all_obs,mt,gg,"no")
gg<-add_plot("E3_0_p1_vev",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_p1_meffl0",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_p1_meffl1",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_p1_meffl2",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_p1_meffl3",all_obs,mt,gg,"no")

######
file_meff=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_meff_correlators",dir,T,L)
#cat("\n####",file_meff,'\n\n')
mt_meff<-read_df(file_meff)
all_obs_meff<- get_all_corr(mt_meff)
gg<-add_plot("E3_0_p1_meff",all_obs_meff,mt_meff,gg,"no",number=96)

fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )


```



```{r}
gg<-ggplot()
df$E3p1cm<- sqrt(df$E3p1^2-(2*pi/df$L)^2)
df$E3p1cmerr<- 2*df$E3p1*df$E3p1err/ sqrt(df$E3p1^2-(2*pi/df$L)^2)

df$E1p1cm<- sqrt(df$E1p1^2-(2*pi/df$L)^2)
df$E1p1cmerr<- 2*df$E1p1*df$E1p1err/ sqrt(df$E1p1^2-(2*pi/df$L)^2)


gg<- gg+ geom_point(data=df,mapping=aes(x=L, y=E3p1cm, color="$3\\phi_0$"))
gg<- gg+ geom_errorbar(data=df,mapping=aes(x=L, ymin=E3p1cm-E3p1cmerr, ymax=E3p1cm+E3p1cmerr, color="$3\\phi_0$"), width=0.3)
gg<- gg+ geom_point(data=df,mapping=aes(x=L, y=E1p1cm, color="$\\phi_1$"))
gg<- gg+ geom_errorbar(data=df,mapping=aes(x=L, ymin=E1p1cm-E1p1cmerr, ymax=E1p1cm+E1p1cmerr, color="$\\phi_1$"), width=0.3)
myplotly(gg,"","L","E_{CM}(p=(1,0,0))",to_print=FALSE)
```


```{r, include=FALSE}
library(ggplot2)
library(plotly)
df <- data.frame(x = 1:5, y = 1:5)    
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knitr handle the rendering naturally
```