
# Fit of the energy levels


```{r , include=FALSE}
library(knitr)
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, result='asis')

#knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.align='center',       comment='')
#knitr::opts_chunk$set(fig.width=8, fig.height=5) 
require(ggplot2)
require(scales) # to access break formatting functions
library(latex2exp)
library(pander)
panderOptions('knitr.auto.asis', FALSE)
library(plotly)
library(reticulate)
use_python("/home/marco/Programs/Anaconda3/bin/python")

# library(knitrengines) # github.com/hrbrmstr/knitrengines
library(dplyr)
library(Rose)
library(ggrepel)
``` 

```{r, echo=FALSE}
file=sprintf("../fit_out/k_from_phase_shift_fit_data.txt")
df<- read.table(file, header=FALSE, fill=TRUE)
names(df) <- c("$L$","$k/m$","err", "$T$","$q2$")
df<- df[c("$T$","$L$","$k/m$","err" ,"$q2$")] 
kable(df[,-5],digit=20)
```

## P = (0,0,0), (1,0,0), (1,1,0)

$$
\frac{k}{m} \cot{ \delta}=\frac{1}{am}+\frac{r_0 m }{2}\frac{k^2}{m^2}
$$
$P[0]=am$ , $P[1]=r_0m$

```{r , child="../fit_out/k_from_phase_shift_fit_P.tex", eval=TRUE}
```

```{r, echo=FALSE}
file=sprintf("../fit_out/M0_finite_vol_fit_out_L.txt")
df_fit<- read.table(file, header=FALSE, fill=TRUE,col.names = c("L","M0L","M0L_err"))
m0=df_fit$M0L[length(df_fit[,1])]

dfree= list()
countfree=1
momenta<-list(c(0,0,0,0,0,0),c(1,0,0,0,0,0),c(1,1,0,0,0,0),c(1,0,0,-1,0,0), c(1,1,1,0,0,0))
for (p in momenta){
  myL<-c()
  myk<-c()
  for (L in c(17:50)){
    norm= p[1]^2+p[2]^2+p[3]^2
    norm=norm*(2*pi/L)^2
    norm1= p[4]^2+p[5]^2+p[6]^2
    norm1=norm1*(2*pi/L)^2
    norm_tot= (p[1]+p[4])^2+(p[2]+p[5])^2+(p[3]+p[6])^2
    norm_tot=norm_tot*(2*pi/L)^2
    E2=sqrt(m0^2+norm1)+ sqrt(m0^2+norm )
    E2cm=sqrt(E2^2-norm_tot)
    k=sqrt(E2cm^2/4. -m0^2)
    s=sprintf("(%d,%d,%d)(%d,%d,%d)",p[1],p[2],p[3],p[4],p[5],p[6])
    myL<-c(myL,L)
    myk<-c(myk,k)
  }
  dfree[[countfree]]<-data.frame("L"=myL,"k"=myk)
  countfree=countfree+1
}
```

```{r, echo=FALSE}
file=sprintf("../fit_out/k_from_phase_shift_fit_data.txt")
df<- read.table(file, header=FALSE, fill=TRUE)
#names(df) <- c("$L$","$k/m$","err", "$T$","$q2$")
#df<- df[c("$T$","$L$","$k/m$","err" ,"$q2$")] 
#kable(df[,-5],digit=20)


gg<- ggplot()
gg<-gg+  geom_point(data=df, mapping=aes(x=df[,1] , y=df[,2],
                          color=as.factor(df[,6])) ,width=0.001)+labs(color = "momuntum")
gg<-gg + geom_errorbar(data=df, mapping=aes(x=df[,1] , ymin=df[,2]-df[,3],
                          ymax=df[,2]+df[,3],color=as.factor(df[,6])) ,width=0.001)

datalist = list()
for (n in c(1:3)){
  
file=sprintf("../fit_out/k_from_phase_shift_fit_out_n%d_L.txt",n-1)
datalist[[n]]<- read.table(file, header=FALSE, fill=TRUE,   
                 col.names=c(paste0("x",n),paste0("fit",n),paste0("fiterr",n)))

gg<-gg + geom_ribbon(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , ymin=datalist[[n]][,2]-datalist[[n]][,3], ymax=datalist[[n]][,2]+datalist[[n]][,3]),fill="blue",alpha=0.5)
gg<-gg + geom_line(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , y=datalist[[n]][,2] ),color="blue" )
gg<-gg + geom_line(data=dfree[[n]], mapping=aes(x=L , y=k/m0 ),color="red" )

#gg<-gg + geom_line(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , y=datalist[[n]][,2] +datalist[[n]][,3]),color=n )
#gg<-gg + geom_line(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , y=datalist[[n]][,2] -datalist[[n]][,3]),color=n )

#gg<-gg + geom_line(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , y=datalist[[n]][,2]+datalist[[n]][,3], color=as.factor(df[,2]) ))
#gg<-gg + geom_text_repel(data=df, mapping=aes(x=L,  y=M0L, label=T))
#gg<- gg + xlim(18 ,36) +ylim(0.145,0.149)
#gg<- gg +labs(x = TeX('k^2'), y= TeX('$k \\cot(\\delta)$'))

}

gg<- gg+theme_bw() #+ ggplot2::coord_cartesian(xlim=c(0,0.05), ylim=c(-3,0 ))


fig<- ggplotly(gg,dynamicTicks = TRUE) #%>%config(mathjax = "cdn")
fig<- fig  %>% layout(title="fit" ,
  xaxis = list(title = "$L$",showexponent = "all", exponentformat = "e" ,range=c(23, 40), autorange = F),
  yaxis = list(title = "$k/m$",showexponent = "all", exponentformat = "e",range=c(0, 1.9), autorange = F)) 

fig
```

## P = (0,0,0), (1,0,0), (1,1,0) , (0,0,0)

```{r , child="../fit_out/k_from_phase_shift_n4_fit_P.tex", eval=TRUE}
```



```{r, echo=FALSE}
file=sprintf("../fit_out/k_from_phase_shift_n4_fit_data.txt")
df<- read.table(file, header=FALSE, fill=TRUE)
#names(df) <- c("$L$","$k/m$","err", "$T$","$q2$")
#df<- df[c("$T$","$L$","$k/m$","err" ,"$q2$")] 
#kable(df[,-5],digit=20)


gg<- ggplot()
gg<-gg+  geom_point(data=df, mapping=aes(x=df[,1] , y=df[,2],
                          color=as.factor(df[,6])) ,width=0.001)+labs(color = "momuntum")
gg<-gg + geom_errorbar(data=df, mapping=aes(x=df[,1] , ymin=df[,2]-df[,3],
                          ymax=df[,2]+df[,3],color=as.factor(df[,6])) ,width=0.001)

datalist = list()
for (n in c(1:4)){
  
file=sprintf("../fit_out/k_from_phase_shift_n4_fit_out_n%d_L.txt",n-1)
datalist[[n]]<- read.table(file, header=FALSE, fill=TRUE,   
                 col.names=c(paste0("x",n),paste0("fit",n),paste0("fiterr",n)))

gg<-gg + geom_ribbon(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , ymin=datalist[[n]][,2]-datalist[[n]][,3], ymax=datalist[[n]][,2]+datalist[[n]][,3]),fill="blue",alpha=0.5)
gg<-gg + geom_line(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , y=datalist[[n]][,2] ),color="blue" )
gg<-gg + geom_line(data=dfree[[n]], mapping=aes(x=L , y=k/m0 ),color="red" )

}

gg<- gg+theme_bw() #+ ggplot2::coord_cartesian(xlim=c(0,0.05), ylim=c(-3,0 ))


fig<- ggplotly(gg,dynamicTicks = TRUE) #%>%config(mathjax = "cdn")
fig<- fig  %>% layout(title="fit" ,
  xaxis = list(title = "$L$",showexponent = "all", exponentformat = "e" ,range=c(23, 40), autorange = F),
  yaxis = list(title = "$k/m$",showexponent = "all", exponentformat = "e",range=c(0, 2.1), autorange = F)) 

fig
```


## P = (0,0,0), (1,0,0), (1,1,0) , (0,0,0) ,(1,1,1)


```{r , child="../fit_out/k_from_phase_shift_n5_fit_P.tex", eval=TRUE}
```



```{r, echo=FALSE}
file=sprintf("../fit_out/k_from_phase_shift_n5_fit_data.txt")
df<- read.table(file, header=FALSE, fill=TRUE)
#names(df) <- c("$L$","$k/m$","err", "$T$","$q2$")
#df<- df[c("$T$","$L$","$k/m$","err" ,"$q2$")] 
#kable(df[,-5],digit=20)


gg<- ggplot()
gg<-gg+  geom_point(data=df, mapping=aes(x=df[,1] , y=df[,2],
                          color=as.factor(df[,6])) ,width=0.001)+labs(color = "momuntum")
gg<-gg + geom_errorbar(data=df, mapping=aes(x=df[,1] , ymin=df[,2]-df[,3],
                          ymax=df[,2]+df[,3],color=as.factor(df[,6])) ,width=0.001)

datalist = list()
for (n in c(1:5)){
  
file=sprintf("../fit_out/k_from_phase_shift_n5_fit_out_n%d_L.txt",n-1)
datalist[[n]]<- read.table(file, header=FALSE, fill=TRUE,   
                 col.names=c(paste0("x",n),paste0("fit",n),paste0("fiterr",n)))

gg<-gg + geom_ribbon(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , ymin=datalist[[n]][,2]-datalist[[n]][,3], ymax=datalist[[n]][,2]+datalist[[n]][,3]),fill="blue",alpha=0.5)
gg<-gg + geom_line(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , y=datalist[[n]][,2]  ), color="blue" )

gg<-gg + geom_line(data=dfree[[n]], mapping=aes(x=L , y=k/m0 ),color="red" )

}

gg<- gg+theme_bw() #+ ggplot2::coord_cartesian(xlim=c(0,0.05), ylim=c(-3,0 ))


fig<- ggplotly(gg,dynamicTicks = TRUE)# %>%config(mathjax = "cdn")
fig<- fig  %>% layout(title="fit" ,
  xaxis = list(title = "$L$",showexponent = "all", exponentformat = "e" ,range=c(23, 40), autorange = F),
  yaxis = list(title = "$k/m$",showexponent = "all", exponentformat = "e",range=c(0, 1.9), autorange = F)) 

fig
```

## 3 parameters fit

$$
\frac{k}{m} \cot{ \delta}=\frac{1}{am}+\frac{r_0 m }{2}\frac{k^2}{m^2}+ \frac{P_2 r_0^3 k^4}{m}
$$



$P[0]=am$ , $P[1]=r_0m$  ,  $P[2]=P_2$


```{r , child="../fit_out/k_from_phase_shift_n5_3par_fit_P.tex", eval=TRUE}
```



```{r, echo=FALSE, results='asis'}
file=sprintf("../fit_out/k_from_phase_shift_n5_3par_fit_data.txt")
df<- read.table(file, header=FALSE, fill=TRUE)
#names(df) <- c("$L$","$k/m$","err", "$T$","$q2$")
#df<- df[c("$T$","$L$","$k/m$","err" ,"$q2$")] 
#kable(df[,-5],digit=20)


gg<- ggplot()
gg<-gg+  geom_point(data=df, mapping=aes(x=df[,1] , y=df[,2],
                          color=as.factor(df[,6])) ,width=0.001)
gg<-gg + geom_errorbar(data=df, mapping=aes(x=df[,1] , ymin=df[,2]-df[,3],
                          ymax=df[,2]+df[,3],color=as.factor(df[,6])) ,width=0.001)
datalist = list()
for (n in c(1:5)){
  
file=sprintf("../fit_out/k_from_phase_shift_n5_fit_out_n%d_L.txt",n-1)
datalist[[n]]<- read.table(file, header=FALSE, fill=TRUE,   
                 col.names=c(paste0("x",n),paste0("fit",n),paste0("fiterr",n)))

gg<-gg + geom_ribbon(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , ymin=datalist[[n]][,2]-datalist[[n]][,3], ymax=datalist[[n]][,2]+datalist[[n]][,3]),fill="blue",alpha=0.5)
gg<-gg + geom_line(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , y=datalist[[n]][,2]  ), color="blue" )
gg<-gg + geom_line(data=dfree[[n]], mapping=aes(x=L , y=k/m0,color="free energy level" ) )


}

gg<- gg+theme_bw() #+ ggplot2::coord_cartesian(xlim=c(0,0.05), ylim=c(-3,0 ))
# gg<-gg +scale_color_manual(labels = c("aaa", "(1,0,0)(0,0,0)","(1,1,0)(0,0,0)","(1,1,1)(0,0,0)","(1,0,0)(-1,0,0)"), values=c("red","red","red","red","red"))

fig<- ggplotly(gg,dynamicTicks = TRUE) #%>%config(mathjax = "cdn")
fig<- fig  %>% layout(title="fit" ,
  xaxis = list(title = "$L$",showexponent = "all", exponentformat = "e" ,range=c(23, 40), autorange = F),
  yaxis = list(title = "$k/m$",showexponent = "all", exponentformat = "e",range=c(0, 1.9), autorange = F)) 

fig
```


## Lattice dispersion relation 

given the parametrization

$$
\frac{k}{m} \cot{ \delta}=\frac{1}{am}+\frac{r_0 k^2}{2m}\,,
$$
with $P[0]=am$ , $P[1]=r_0 m$  ,  $P[2]=P_2$. We solve the quantization condition 
finding the value of $k$ such that 
$$
\cot{ \delta}=\frac{Z_{00}(1,q^2)}{\pi^{3/2}\gamma q}.
$$

From k we compute the two particle energy  $E_2$

$$
k^2=\frac{E_{CM}^2}{4}-m^2 = \frac{E^2-\vec{P}^2}{4}-m^2.
$$

and finally the energy shift 
$$
   \Delta E_2^{predicted} = E_2 - \sqrt{4m^2 + p_1^2}-\sqrt{4m^2 + p_2^2} 
$$

On the other hand we measure the two particle energy and we compute the energy shift 
with the lattice dispersion relation
$$
\Delta E_2^{latt}=E_2^{measured}-E_2^{free-latt} 
$$
\begin{gather}
    E_2^{free-latt} = \cosh^{-1}{\left( \cosh(m) +\frac{1}{2}\left( \sum_{i=1}^{2}4 \sin\left(\frac{ p_{1i}}{2}\right)^2\right)\right)} \\
    +     \cosh^{-1}{\left( \cosh(m) +\frac{1}{2}\left(  \sum_{i=1}^{2}4 \sin\left(\frac{ p_{2i}}{2}\right)^2\right)\right)} \,.  
    (\#eq:E2-free-latt)
\end{gather}

Finally we minimise the $\chi^2$
$$
\chi^2= \sum_i   \frac{( \Delta E_2^{predicted}  -\Delta E_2^{latt})^2}{\sigma^2}
$$



```{r , child="../fit_out/deltaE2_m_quant_cond_fit_P.tex", eval=TRUE}
```





```{r, echo=FALSE, results='asis'}
file=sprintf("../fit_out/deltaE2_m_quant_cond_fit_data.txt")
df<- read.table(file, header=FALSE, fill=TRUE)
#names(df) <- c("$L$","$k/m$","err", "$T$","$q2$")
#df<- df[c("$T$","$L$","$k/m$","err" ,"$q2$")] 
#kable(df[,-5],digit=20)

gg<- ggplot()
gg<-gg+  geom_point(data=df, mapping=aes(x=df[,1] , y=df[,2],
                          color=as.factor(df[,6]), shape=as.factor(df[,6])) ,width=0.001)+labs(color = "momentum", shape="momentum")
gg<-gg + geom_errorbar(data=df, mapping=aes(x=df[,1] , ymin=df[,2]-df[,3],
               ymax=df[,2]+df[,3],color=as.factor(df[,6]),shape=as.factor(df[,6]) ) ,width=0.001)
mom_lab<-function(vec){
  count=1
  r<- c()
  for(v in vec){
    if(v==0)
      r[count]="(0,0,0)"
    else if(v==1)
      r[count]="(1,0,0)"
    else if(v==2)
      r[count]="(1,1,0)"
    else if(v==3)
      r[count]="(1-1,0,0)"
    else if(v==4)
      r[count]="(1,1,1)"
    else
      r[count]="boh"
    count=count+1
  }
  return(r)
}
df[,6]<-mom_lab(df[,6])
datalist = list()
for (n in c(1:5)){
  
file=sprintf("../fit_out/deltaE2_m_quant_cond_fit_out_n%d_L.txt",n-1)
datalist[[n]]<- read.table(file, header=FALSE, fill=TRUE,   
                 col.names=c(paste0("x",n),paste0("fit",n),paste0("fiterr",n)))

gg<-gg + geom_ribbon(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , ymin=datalist[[n]][,2]-datalist[[n]][,3], ymax=datalist[[n]][,2]+datalist[[n]][,3]),alpha=0.5, fill="blue")
gg<-gg + geom_line(data=datalist[[n]], mapping=aes_string(x=datalist[[n]][,1] , y=datalist[[n]][,2]  ),color="blue" )
#as.factor(n-1)
#gg<-gg + geom_line(data=dfree[[n]], mapping=aes(x=L , y=k/m0 ),color="red" )


}

gg<- gg+theme_bw() #+ ggplot2::coord_cartesian(xlim=c(0,0.05), ylim=c(-3,0 ))


# fig<- ggplotly(gg,dynamicTicks = TRUE)# %>%config(mathjax = "cdn")
# fig<- fig  %>% layout(title="fit" ,
#   xaxis = list(title = "$L$",showexponent = "all", exponentformat = "e" ,range=c(26, 40), autorange = F),
#   yaxis = list(title = "$E_2- E_{free}^{lat}+E_{free}^{cont}/m$",showexponent = "all", exponentformat = "e"))#,range=c(0, 1.9), autorange = F)) 

fig_pdf<- myplotly(gg,"", "$L$", "$E_2- E_{free}^{lat}+E_{free}^{cont}/m$", xrange=c(26, 40),yrange=c(2,4.5), output="PDF",to_print = FALSE)
#library(ggforce)
#fig_pdf<- fig_pdf+ facet_zoom(ylim = c(2.65, 2.75))
save_pdf = "pdf_figs/E2_latt_fit"
      texfile=paste0(save_pdf,".tex")
      tikzDevice::tikz(texfile,standAlone=TRUE, width = 8, height = 4)
      plot(fig_pdf)
      dev.off()
      tools::texi2dvi(paste0(save_pdf,".tex"),pdf=TRUE)

fig<- myplotly(gg,"fit", "L", "$E_2- E_{free}^{lat}+E_{free}^{cont}/m$", xrange=c(23, 40) , yrange=c(1.8,5))


```

the resulting $\delta$ determined is

```{r, echo=FALSE, results='asis'}
file=sprintf("../fit_out/deltaE2_m_quant_cond_fit_phase_shift.txt")
df<- read.table(file, header=FALSE, fill=TRUE)


gg<- ggplot()
gg<-gg+  geom_ribbon(data=df, mapping=aes(x=df[,1] , ymin=df[,2]-df[,3], ymax=df[,2]+df[,3]), color=NA, fill="blue")

gg<- gg+theme_bw() 
fig<-myplotly(gg,"","$k/M_0$","$\\delta$",to_print=TRUE)

```