
# report fit phase shift $\delta$

```{r , include=FALSE}
library(knitr)
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, result='asis')

#knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.align='center',       comment='')
knitr::opts_chunk$set(fig.width=8, fig.height=5) 
require(ggplot2)
require(scales) # to access break formatting functions
library(latex2exp)
library(pander)
panderOptions('knitr.auto.asis', FALSE)
library(plotly)
library(reticulate)
use_python("/home/marco/Programs/Anaconda3/bin/python")

# library(knitrengines) # github.com/hrbrmstr/knitrengines
library(dplyr)
library(Rose)
library(ggrepel)

``` 




The phase shif can be computed from the formula

$$
\cot{ \delta}=\frac{Z_{00}(1,q^2)}{\pi^{3/2}\gamma q}
$$
where $\gamma=E/E_{CM}$, $q=kL/2\pi$ with  $k$ the scattering momentum
$$
k^2=\frac{E_{CM}^2}{4}-m^2 = \frac{E^2-\vec{P}^2}{4}-m^2.
$$
The Energy in the center of mass is related to the one in a generic frame with toal momentum $\vec{P}$ via
$$
E_{CM}^2=E^2-\vec{P}^2\,.
$$
For the $Z$ function we use the rzeta package.
The fit function for the phase shift is 
$$
k \cot{ \delta}=\frac{1}{a}+\frac{r_0 k^2}{2}-Pr_0^3 k^4
$$


```{r, echo=FALSE, result='asis' ,dev='tikz', warning=FALSE}
file=sprintf("../fit_out/kcotd_fit_data.txt")
df<- read.table(file, header=FALSE, fill=TRUE)
names(df) <- c("$L$","$k \\cot(\\delta)$","err", "$T$","$k$")
df<- df[c("$T$","$L$","$k \\cot(\\delta)$","err" ,"$k$")] 
df$"$q^2$"<-(df[,5]*df[,2]/(2*pi))^2
kable(df,digit=20)

file=sprintf("../fit_out/M0_finite_vol_fit_out_L.txt")
df_fit<- read.table(file, header=FALSE, fill=TRUE,col.names = c("L","M0L","M0L_err"))
m0=df_fit$M0L[length(df_fit[,1])]
```


```{r , child="../fit_out/kcotd_fit_P.tex", eval=TRUE}
```

```{r,echo=FALSE, result='asis' ,dev='tikz', warning=FALSE}
file=sprintf("../fit_out/kcotd_fit_out_k.txt")
df_fit<- read.table(file, header=FALSE, fill=TRUE,col.names = c("x","fit","fiterr"))
gg<- ggplot()
gg<-gg+  geom_point(data=df, mapping=aes(x=df[,5]^2 , y=df[,3],
                          color=as.factor(df[,2])) ,width=0.001)+labs(color = "L")
gg<-gg + geom_errorbar(data=df, mapping=aes(x=df[,5]^2 , ymin=df[,3]-df[,4],
                          ymax=df[,3]+df[,4],color=as.factor(df[,2])) ,width=0.001)
gg<-gg + geom_ribbon(data=df_fit, mapping=aes(x=x*x , ymin=fit-fiterr, ymax=fit+fiterr),fill="blue",alpha=0.2)
gg<-gg + geom_line(data=df_fit, mapping=aes(x=x*x , y=fit),fill="blue")

#gg<-gg + geom_text_repel(data=df, mapping=aes(x=L,  y=M0L, label=T))
#gg<- gg + xlim(18 ,36) +ylim(0.145,0.149)
#gg<- gg +labs(x = TeX('k^2'), y= TeX('$k \\cot(\\delta)$'))

gg<- gg+theme_bw() #+ ggplot2::coord_cartesian(xlim=c(0,0.05), ylim=c(-3,0 ))


# fig<- ggplotly(gg,dynamicTicks = TRUE)# %>%config(mathjax = "cdn")
# fig<- fig  %>% layout(title="fit" ,xaxis = list(title = TeX("k^2"),showexponent = "all", exponentformat = "e" , range=c(-0.001, 0.06), autorange = F  ) ,
#                       yaxis = list(title = TeX("k \\cot\\delta"),showexponent = "all", exponentformat = "e", range=c(-3,-0.5), autorange = F  )) 
# 
# fig
fig<-myplotly(gg,"fit","$k^2$","$k \\cot\\delta$",c(-0.001, 0.06), c(-3,-0.5),to_print=FALSE  )
fig
```



### Lattice dispersion relation

We correct the energy with

$$
   E_2=E_2^{measured}-E_2^{free-latt}+E_2^{free-cont}
$$
with $E_2^{free-latt}$ defined in \@ref(eq:E2-free-latt)


```{r, echo=FALSE}
file=sprintf("../fit_out/kcotd_Elatt_fit_data.txt")
df<- read.table(file, header=FALSE, fill=TRUE)
names(df) <- c("$L$","$k \\cot(\\delta)$","err", "$T$","$k$")
df<- df[c("$T$","$L$","$k \\cot(\\delta)$","err" ,"$k$")] 
df$"$q^2$"<-(df[,5]*df[,2]/(2*pi))^2
kable(df,digit=20)
```


```{r , child="../fit_out/kcotd_Elatt_fit_P.tex", eval=TRUE}
```

```{r,echo=FALSE}
file=sprintf("../fit_out/kcotd_Elatt_fit_out_k.txt")
df_fit<- read.table(file, header=FALSE, fill=TRUE,col.names = c("x","fit","fiterr"))
gg<- ggplot()
gg<-gg+  geom_point(data=df, mapping=aes(x=df[,5]^2 , y=df[,3],
                          color=as.factor(df[,2])) ,width=0.001)+labs(color = "L")
gg<-gg + geom_errorbar(data=df, mapping=aes(x=df[,5]^2 , ymin=df[,3]-df[,4],
                          ymax=df[,3]+df[,4],color=as.factor(df[,2])) ,width=0.001)
gg<-gg + geom_ribbon(data=df_fit, mapping=aes(x=x*x , ymin=fit-fiterr, ymax=fit+fiterr),fill="blue",alpha=0.2)
gg<-gg + geom_line(data=df_fit, mapping=aes(x=x*x , y=fit),fill="blue")

#gg<-gg + geom_text_repel(data=df, mapping=aes(x=L,  y=M0L, label=T))
#gg<- gg + xlim(18 ,36) +ylim(0.145,0.149)
#gg<- gg +labs(x = TeX('k^2'), y= TeX('$k \\cot(\\delta)$'))

gg<- gg+theme_bw() #+ ggplot2::coord_cartesian(xlim=c(0,0.05), ylim=c(-3,0 ))

# 
# fig<- ggplotly(gg,dynamicTicks = TRUE)# %>%config(mathjax = "cdn")
# fig<- fig  %>% layout(title="fit" ,xaxis = list(title = TeX("k^2"),showexponent = "all", exponentformat = "e" , range=c(-0.001, 0.06), autorange = F  ) ,
#                       yaxis = list(title = TeX("k \\cot\\delta"),showexponent = "all", exponentformat = "e", range=c(-3,-0.5), autorange = F  )) 

fig<-myplotly(gg,"fit","$k^2$","$k \\cot\\delta$",c(-0.001, 0.06), c(-3,-0.5),to_print=FALSE  )
fig
```
