# Smearing



```{r, include=FALSE}
library(ggplot2)
library(plotly)
df <- data.frame(x = 1:5, y = 1:5)    
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knitr handle the rendering naturally
```

in order to have a field with the same quantum number of $\phi_0$ we create the smeared field
$$
  S_{n+1}(x,p)=e^{i\rho S_n(x,p)}S_n(x,p)\,\quad\quad \mbox{with}\quad\quad S_0=\phi_0\,,
$$
and $n=5$ and $\rho=0.2$.
Then we compute the correlator
$$
\langle S_n(0,p=0) S_n(t,p=0) \rangle
$$

```{r, echo=FALSE,results='asis'}


gg<-ggplot()
T<- 32
L<- 24
# dir<-paste("../out")
# file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)
dir<-paste("../../momentum/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)

mt<-read_df(file)
all_obs<- get_all_corr(mt)

 # gg<-add_plot("GEVP_phi0_phi03_phi1_meffl0",all_obs,mt,gg,"no")
 # gg<-add_plot("GEVP_phi0_phi03_phi1_meffl1",all_obs,mt,gg,"no")
 # gg<-add_plot("GEVP_phi0_phi03_phi1_meffl2",all_obs,mt,gg,"no")
 gg<-add_plot("E1_0",all_obs,mt,gg,"no")
# gg<-add_plot("sE1_0",all_obs,mt,gg,"no")
 # gg<-add_plot("E3_0",all_obs_meff,mt_meff,gg,"no",6)

fig<- myplotly(gg,"fit","t", "$m_{eff}$", to_print=TRUE )


```


## Gaussian Smearing 

Following [@Montvay_2012] we can define the smeared field 
$$
  S(t,x)=\sum_{y_i:|x_i,y_i|<R} \phi(t,y) e^{-\rho \sum_i |x_i,y_i|^2 }
$$

with $|x,y|=\min\{ |x-y|, |x-y+L|, |x-y-L|\}$.
The projected smeared field to zero momentum
$$
  \tilde S(t,P=0)=\sum_{x_i}\sum_{y_i:|x_i,y_i|<R} \phi(t,y) e^{-\rho \sum_i |x_i,y_i| }=\sum_{\vec x}\sum_{|\vec\mu|<R} \phi(t,\vec x+\vec\mu) e^{-\rho | \vec \mu| }\\
=  \sum_{|\vec\mu|<R}\sum_{\vec x} \phi(t, \vec x+\vec\mu) e^{-\rho | \vec \mu| }
=  \sum_{|\vec\mu|<R} \tilde\phi(t, p=0) e^{-\rho | \vec \mu| }\\
=\tilde\phi(t, p=0) \sum_{|\vec\mu|<R}  e^{-\rho | \vec \mu| }
$$
where we introduce the vector $\vec\mu=| x , y |$ and we use the fact that 
$\sum_{\vec x} \phi(t,\vec x +\vec \mu)=\sum_{\vec x} \phi(t,\vec x )$.

Thus we have that correlation function of the smeared field at zero momentum are 
proportional to the correlation function of the non-smeared field

$$
\langle \tilde S(t,P=0)\tilde S(0,P=0)\rangle
=N \langle \tilde \phi(t,P=0)\tilde \phi(0,P=0)\rangle
$$
Below we compare the effective mass of the correlators

- $\langle \tilde \phi(t,P=0)\tilde \phi(0,P=0)\rangle$ with label E1_0
- $\langle \tilde S(t,P=0)\tilde S(0,P=0)\rangle$ with label sE1_0

in a L4T16 lattice

```{r, echo=FALSE,results='asis' ,dev='tikz'}
library(Rose)
gg<-ggplot()
T<- 64
L<- 28
 #dir<-paste("/home/marco/programs/Z2-phi4/build/main/data/out")
 #file=sprintf("%s/G2t_T%d_L%d_msq0-4.850000_msq1-4.850000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)
 dir<-paste("../../g0.025/out")
 file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.025000_rep0_output",dir,T,L)
 
cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)



gg<-add_plot("E1_0",all_obs,mt,gg,"no")
gg<-add_plot("sE1_0",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", width=900, yrange = c(-3,5) )


```

```{r, echo=FALSE,results='asis' ,dev='tikz'}
gg<-ggplot()



gg<-add_plot("E1_0_p1",all_obs,mt,gg,"no")
gg<-add_plot("sE1_0_p1",all_obs,mt,gg,"no")


fig<- myplotly(gg,"fit","t", "y", width=900, yrange = c(-1,3) )


```



```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 128
L<- 24
dir<-paste("../../momentum/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl0",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl1",all_obs,mt,gg,"no")
gg<-add_plot("GEVP_phi0_phi03_phi1_p1_meffl2",all_obs,mt,gg,"no")
gg<-add_plot("E1_0_p1",all_obs,mt,gg,"no")
gg<-add_plot("E1_1_px",all_obs,mt,gg,"no")
#gg<-add_plot("E3_0_p1_vev",all_obs,mt,gg,"no")
gg<-add_plot("sE1_0_p1",all_obs,mt,gg,"no")
#gg<-add_plot("E2_0_p0",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_p1_meffl0",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_p1_meffl1",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_p1_meffl2",all_obs,mt,gg,"no")
#gg<-add_plot("GEVP_0_3_1_A1_p1_meffl3",all_obs,mt,gg,"no")

######
# file_meff=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_meff_correlators",dir,T,L)
# #cat("\n####",file_meff,'\n\n')
# mt_meff<-read_df(file_meff)
# all_obs_meff<- get_all_corr(mt_meff)
# gg<-add_plot("E3_0_p1_meff",all_obs_meff,mt_meff,gg,"no",number=96)

fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )


```





```{r, echo=FALSE,results='asis'}

gg<-ggplot()
T<- 128
L<- 24
dir<-paste("../../momentum/out")
file=sprintf("%s/G2t_T%d_L%d_msq0-4.900000_msq1-4.650000_l02.500000_l12.500000_mu5.000000_g0.000000_rep0_output",dir,T,L)

cat("\n####",file,'\n\n')

mt<-read_df(file)
all_obs<- get_all_corr(mt)

gg<-add_plot("E2_0",all_obs,mt,gg,"no")
gg<-add_plot("sE2_0",all_obs,mt,gg,"no")
gg<-add_plot("E2_0_p0",all_obs,mt,gg,"no")

fig<- myplotly(gg,"fit","t", "y", to_print=TRUE,width = 900 )


```


## Laplace smearing

We introduce a fictitious smearing time $\tau$ and we solve
$$
 \partial_\tau \phi(\tau,t,\vec x)=\nabla^2 \phi(\tau,t,\vec x)
 \,\quad\mbox{with}\,\quad
 \phi(0,t,\vec x)=\phi(t,\vec x)\,.
$$
this smearing do not effect the zero momentum component because the laplacian $\nabla^2=\partial_{x_1}^2+\partial_{x_2}^2+\partial_{x_3}^2$ in momentum space is zero
$$
 \partial_\tau \tilde\phi(\tau,t,\vec p)=|\vec{p}|^2 \tilde\phi(\tau,t,\vec p)
$$



